### 2021-05-10 yfcc100m/paper/vldb2021/eval.tex
Minor updates to eval

Given that there are no other open-source systems that provide similar
functionality and interfaces as VDMS (i.e., transactionally dealing with images
and metadata behind a single interface), we have implemented two equivalent
visual data management system as baselines,
design specifically for the image search use case,
and comprised of a combination of widely available, off-the-shelf components.
The first baseline uses MySQL Server 5.7 (for storing metadata),
Apache Web Server 2.4.18 (as interface for image access), and
OpenCV 3.3 (to provide pre-processing operations on images).
We chose Apache Web Server to work as a file server (serving the image files),
because it provides the lowest possible overhead
(when compared to other object store system), at the expenses of providing less
functionality (authentication, data integrity checking, etc).
The other baseline system replaces the MySQL Server 5.7 with a
most advanced open-source relational database, PostgreSQL 9.5 \cite{postgresql}.
We decided to use relational databases in the baseline systems instead of
non-relational databases because of their maturity, and also because it is
the most common tools used for storing and querying metadata
~\cite{Jatana2012, li_2019}:

@@

In the case of VDMS, we see the performance in the case of \textit{q3}
and \textit{q5} suffers significantly in comparison to the other queries.
The reason for that lack of scalability lies on the query implementation: given that
VDMS does not yet support operators that enable querying images
that have both connections to a \textit{tagA} and a \textit{tagB};
we have to implement this transaction by doing 2 retrievals.
This involves retrieving partial information in the first retrieval,
applying an INTERSECTION operation in the client, and doing a second retrieval
to bring the right metadata and/or images.
The reason for this is a lack of operations that would enable this query to be
run entirely on the server is not an inherent limitation to VDMS but rather
just a missing implementation.
In the case of \textit{q4} and \textit{q6}, it is worth noting
that for the OR operation, there is no need for 2 retrievals (2 transactions).
Rather, a single transaction is performed and the result filtered on the client.
Future VDMS releases will add more of such operators (AND, OR, etc)
in order to prevent unnecessary retrievals and extra filtering on the client side.

@@

We designed VDMS with the idea in mind that pre-processing operations will be
commonly performed, as visual data is generally pre-processed before analytics
computation are performed on them (i.e., a resize plus
normalization done on images before passing them through a neural network).
Figure \ref{fig:q_throughput_56_resize} shows how the query throughput varies
when a pre-processing operations is applied (in this case, a resize operation).
The first thing to notice is that a resize operation is a significant part of
the overall operation (retrieval + preprocessing).
Doing a resize operation as part of the retrieval process
brings the throughput down by orders of magnitude.
This is the case for both VDMS and the baselines.
Nonetheless, VDMS is orders of magnitude faster when retrieving images
both with and without resize operations.
An important thing to notice is that, even if a resized image is smaller,
and thus transfered faster between the server and the client,
transferring the image as is (without resize) is faster in this case.
This is a characteristic of the dataset, which has relatively small images
(the average image is about 150KB in size).
We have seen on other applications and datasets with higher resolution images
that transferring resized (or cropped) images is significantly faster than
transferring images as they are stored.
An interesting aspect to notice is that, when removing the resize operations,
differences between the 2 baseline systems become more noticeable.
For instance, for an image retrieval based on a single tag, we see how
\textit{postgresql} outperforms \textit{mysql}, but when adding geo-location
filtering, we see \textit{mysql} showing a small advantage.
When the resize operations is performed, both baselines do very similar
on 1tag based queries, and orders of magnitude worst than VDMS.
Note that in the baseline systems, the resize happens on the client side,
rather than on the server side.
This is the common case in most analytics applications, where pre-processing
operations happen on the client side (or wherever the analytics computation happens),
rather than near where the data is located, as it is the case with VDMS.
We kept both the server and client systems the same to avoid the computation
capabilities difference complicating our understanding of the results.

@@

Finally, Figure~\ref{fig:summary_postgresql} summarizes the results
comparing VDMS and \textit{postgresql}.
In comparison to \textit{postgresql}, VDMS provides up to 364x speedup
(for the case of \textit{q1}),
and an average improvement in throughput of about 85x.
This is an impressive improvement over the two baseline systems.
More importantly, we see that the speedup increases as the database size grows,
showing that VDMS scales better than the baseline systems.
We also see how \textit{q3} and \textit{q5} have poor performances and scalability
when compared to the baselines as the database size grows, except in the
case of the largest database (100M), where the baselines performed very poorly.
This evaluation served the
purpose of understanding the importance of VDMS server side operators
that enable more complex queries for our use cases.
The team will address the missing implementation as part of future work.
Most of the performance improvements can be attributed to the design
principles of VDMS, which aims to eliminate the need of combining and
re-purposing systems that were designed to handle types of date other than visual.
VDMS, by design, eliminates most of the inefficiencies that result
from a forced integration of components designed for a
different range of applications.

>>>>

Given that there are no other open-source systems that provide similar
functionality and interfaces as VDMS (i.e., transactionally dealing with images
and metadata behind a single interface), we have implemented two equivalent
visual data management system as baselines,
design specifically for the image search use case,
and comprised of a combination of widely available, off-the-shelf components.
The first baseline uses MySQL Server 5.7 (for storing metadata),
Apache Web Server 2.4.18 (as interface for image access), and
OpenCV 3.3 (to provide pre-processing operations on images).
We chose Apache Web Server to work as a file server (serving the image files),
because it provides the lowest possible overhead
(when compared to other object store system), at the expenses of providing less
functionality (authentication, data integrity checking, etc.).
The other baseline system replaces the MySQL Server 5.7 with a
most advanced open-source relational database, PostgreSQL 9.5 \cite{postgresql}.
We decided to use relational databases in the baseline systems instead of
non-relational databases because of their maturity, and also because it is
the most common tools used for storing and querying metadata
~\cite{Jatana2012, li_2019}:

@@

In the case of VDMS, we see the performance in the case of \textit{q3}
and \textit{q5} suffers significantly in comparison to the other queries.
The reason for that lack of scalability lies on the query implementation: given that
VDMS does not yet support operators that enable querying images
that have both connections to a \textit{tagA} and a \textit{tagB};
we have to implement this transaction by doing 2 retrievals.
This involves retrieving partial information in the first retrieval,
applying an INTERSECTION operation in the client, and doing a second retrieval
to bring the right metadata and/or images.
The reason for this is a lack of operations that would enable this query to be
run entirely on the server is not an inherent limitation to VDMS but rather
just a missing implementation.
In the case of \textit{q4} and \textit{q6}, it is worth noting
that for the OR operation, there is no need for 2 retrievals (2 transactions).
Rather, a single transaction is performed and the result filtered on the client.
Future VDMS releases will add more of such operators (AND, OR, etc.)
in order to prevent unnecessary retrievals and extra filtering on the client side.

@@

We designed VDMS with the idea in mind that pre-processing operations will be
commonly performed, as visual data is generally pre-processed before analytics
computation are performed on them (i.e., a resize plus
normalization done on images before passing them through a neural network).
Figure \ref{fig:q_throughput_56_resize} shows how the query throughput varies
when a pre-processing operations is applied (in this case, a resize operation).
The first thing to notice is that a resize operation is a significant part of
the overall operation (retrieval + preprocessing).
Doing a resize operation as part of the retrieval process
brings the throughput down by orders of magnitude.
This is the case for both VDMS and the baselines.
Nonetheless, VDMS is orders of magnitude faster when retrieving images
both with and without resize operations.
An important thing to notice is that, even if a resized image is smaller,
and thus transfered faster between the server and the client,
transferring the image as is (without resize) is faster in this case.
This is a characteristic of the dataset, which has relatively small images
(the average image is about 150KB in size).
We have seen on other applications and datasets with higher resolution images
that transferring resized (or cropped) images is significantly faster than
transferring images as they are stored.
An interesting aspect to notice is that, when removing the resize operations,
differences between the 2 baseline systems become more noticeable.
For instance, for an image retrieval based on a single tag, we see how
\textit{postgresql} outperforms \textit{mysql}, but when adding geo-location
filtering, we see \textit{mysql} showing a small advantage.
When the resize operation is performed, both baselines do very similar
on 1tag based queries, and orders of magnitude worst than VDMS.
Note that in the baseline systems, the resize happens on the client side,
rather than on the server side.
This is the common case in most analytics applications, where pre-processing
operations happen on the client side (or wherever the analytics computation happens),
rather than near where the data is located, as it is the case with VDMS.
We kept both the server and client systems the same to avoid the computation
capabilities difference complicating our understanding of the results.

@@

Finally, Figure~\ref{fig:summary_postgresql} summarizes the results
comparing VDMS and \textit{postgresql}.
In comparison to \textit{postgresql}, VDMS provides up to 364x speedup
(for the case of \textit{q1}),
and an average improvement in throughput of about 85x.
This is an impressive improvement over the two baseline systems.
More importantly, we see that the speedup increases as the database size grows,
showing that VDMS scales better than the baseline systems.
We also see how \textit{q3} and \textit{q5} have poor performances and scalability
when compared to the baselines as the database size grows, except in the
case of the largest database (100M), where the baselines performed very poorly.
This evaluation served the
purpose of understanding the importance of VDMS server side operators
that enable more complex queries for our use cases.
The team will address the missing implementation as part of future work.
Most of the performance improvements can be attributed to the design
principles of VDMS, which aims to eliminate the need of combining and
re-purposing systems that were designed to handle types of data other than visual.
VDMS, by design, eliminates most of the inefficiencies that result
from a forced integration of components designed for a
different range of applications.
